### 2017-02-01 conclusion.tex
Fixed some citations due to referee report

The MUGS2 simulations produced in chapter 4 contains a wealth of data
that is useful for future studies. Chapter 5 applied the MUGS2 sample of
galaxies we produced in \citet{Keller2016a} and used them to examine the radial
acceleration relation (RAR) that was derived by \citet{McGaugh2016} from
observations of the SPARC \citep{Lelli2016} catalog.  Contrary to the assertions
of some \citep{Milgrom2016}, the tight relation seen in the SPARC data does not
require new fundamental physics (such as self-interacting dark matter, modified
gravity, or MOND).  Instead, the simple combination of dissipational collapse,
together with angular momentum conservation produces the RAR. This means that
even galaxies where SN fails to regulate their star formation (or even where SN
are omitted altogether) fall on the observed relation.  This was the first
published demonstration of this in simulation, using untuned simulations made
prior to the publication of \citet{McGaugh2016}.

>>>>

The MUGS2 simulations produced in chapter 4 contains a wealth of data
that is useful for future studies. Chapter 5 applied the MUGS2 sample of
galaxies we produced in \citet{Keller2016a} and used them to examine the radial
acceleration relation (RAR) that was derived by \citet{McGaugh2016} from
observations of the SPARC \citep{Lelli2016b} catalog.  Contrary to the assertions
of some \citep{Milgrom2016}, the tight relation seen in the SPARC data does not
require new fundamental physics (such as self-interacting dark matter, modified
gravity, or MOND).  Instead, the simple combination of dissipational collapse,
together with angular momentum conservation produces the RAR. This means that
even galaxies where SN fails to regulate their star formation (or even where SN
are omitted altogether) fall on the observed relation.  This was the first
published demonstration of this in simulation, using untuned simulations made
prior to the publication of \citet{McGaugh2016}.

### 2017-02-01 intro.tex
Julio's typo suggestions
Fixed some citations due to referee report

\section{This Work and Organization of Chapters}
In this thesis, I present a new sub-grid model for the feedback from massive
stars.  I use that model to investigate how this feedback can regulate the
formation of stars within galaxies, and finally show how this same feedback is
unnecessary to produce galaxies that match the observations of
\citet{McGaugh2016}.  I conclude with a summary of these results, their
implications, and some potential future directions for study.

@@

Chapter 5 uses the sample of galaxies developed in the previous chapter to
test whether recent observational results presented in \citet{McGaugh2016}
are consistent with $\Lambda CDM$.  The radial acceleration relation (RAR) seen in
the SPARC sample \citep{Lelli2016} of observed rotationally supported galaxies
shows that the accelerations within these galaxies are tightly correlated 
with the accelerations due to baryons alone.  We show, using the sample of
galaxies generated in chapter 4, that this relation simply falls out of the
dissipative collapse of baryons in a collisionless dark matter halo.  We also
show that this result is independent of stellar feedback.  Despite the insensitivity
to feedback processes at $z=0$, we show that feedback does result in evolution
of the RAR with redshift, and predict that a different RAR would be observed if
a similar study to \citet{Lelli2016} were done for high-redshift galaxies.

>>>>

\section{This Work and Organization of Chapters}
In this thesis, I present a new sub-grid model for the feedback from massive
stars.  I use that model to investigate how this feedback can regulate the
formation of stars within galaxies, and finally show how this same feedback is
unnecessary to produce galaxies that match the observations of
\citet{McGaugh2016} at $z=0$.  I conclude with a summary of these results, their
implications, and some potential future directions for study.

@@

Chapter 5 uses the sample of galaxies developed in the previous chapter to
test whether recent observational results presented in \citet{McGaugh2016}
are consistent with $\Lambda CDM$.  The radial acceleration relation (RAR) seen in
the SPARC sample \citep{Lelli2016b} of observed rotationally supported galaxies
shows that the accelerations within these galaxies are tightly correlated 
with the accelerations due to baryons alone.  We show, using the sample of
galaxies generated in chapter 4, that this relation simply falls out of the
dissipative collapse of baryons in a collisionless dark matter halo.  We also
show that this result is independent of stellar feedback.  Despite the insensitivity
to feedback processes at $z=0$, we show that feedback does result in evolution
of the RAR with redshift, and predict that a different RAR would be observed if
a similar study to \citet{Lelli2016b} were done for high-redshift galaxies.
